R for Clinical Study Reports and Submission

### 2021-08-29 tlf-overview.Rmd
update minor formating item

```{r}
library(r2rtf)

r2rtf_adae %>%
  select(USUBJID, TRTA, AEDECOD) %>%
  head(4)
```
`dplyr` and `tidyr` packages within `tidyverse` are used 
for data manipulation to create a data frame 
that contains all the information we want to add in an RTF table.

```{r}
library(tidyr)
library(dplyr)

tbl <- r2rtf_adae %>%
  count(TRTA, AEDECOD) %>%
  pivot_wider(names_from = TRTA, values_from = n, values_fill = 0)

>>>>

```{r}
r2rtf_adae %>%
  select(USUBJID, TRTA, AEDECOD) %>%
  head(4)
```
`dplyr` and `tidyr` packages within `tidyverse` are used 
for data manipulation to create a data frame 
that contains all the information we want to add in an RTF table.

```{r}
tbl <- r2rtf_adae %>%
  count(TRTA, AEDECOD) %>%
  pivot_wider(names_from = TRTA, values_from = n, values_fill = 0)
